The Etiology of Cybersecurity

### 2021-01-18 reports/paper_0/main.tex
add names to paper
shorten intro

\author{
%	\IEEEauthorblockN{Marco Rocchetto}
%\IEEEauthorblockA{V-Research\\
%Verona, Italy\\
%Email: marco@v-research.it}
%\and
%\IEEEauthorblockN{Francesco Beltramini}
%\IEEEauthorblockA{V-Research\\
%Verona, Italy\\
%Email: francesco@v-research.it}
}

@@

As
Herley mentions in \autocite{Herley2016usenixvideo}, the problem is in the way
we reason on cybersecurity, and we can see it in the way we reply to simple
cybersecurity (foundamental) questions.  Let us consider the general question
``what is cybersecurity?''; as in \autocite{hintikka2013inquiry}, we can
translate the wh-question into an equivalent existentially quantified formula.
But if the formula is $\exists P. P(s)\rightarrow Secure(s)$, (where we ask if
there exists a predicate $P$ such that, given any arbitrary system $s$, when
$P$ holds for $s$ then $s$ can be considered secure), when the answer is (for
example) ``if the system is confidential, the system is secure'' the formula
becomes tautological. In fact, $P$ and $Secure$ can be considered as
semantically equivalent (cybersecurity is confidentiality and vice-versa).

>>>>

\author{
	\IEEEauthorblockN{Marco Rocchetto}
\IEEEauthorblockA{V-Research\\
Verona, Italy\\
Email: marco@v-research.it}
\and
\IEEEauthorblockN{Francesco Beltramini}
\IEEEauthorblockA{V-Research\\
Verona, Italy\\
Email: francesco@v-research.it}
}

@@

%As
%Herley mentions in \autocite{Herley2016usenixvideo}, the problem is in the way
%we reason on cybersecurity, and we can see it in the way we reply to simple
%cybersecurity (foundamental) questions.  Let us consider the general question
%``what is cybersecurity?''; 
%%as in \autocite{hintikka2013inquiry}, we can
%%translate the wh-question into an equivalent existentially quantified formula.
%%But if the formula is $\exists P. P(s)\rightarrow Secure(s)$, 
%%(where we ask if
%if we detail the question as:
%there exists a predicate $P$ such that, given any arbitrary system $s$, when
%$P$ holds for $s$ then $s$ can be considered secure?
%%), 
%When the answer is (for
%example) ``if the system is confidential, the system is secure'' the reasoning %formula
%becomes tautological. In fact, $P$ and $Secure$ can be considered as
%semantically equivalent (cybersecurity is confidentiality and vice-versa).
